### Job Title:
Research Associate in High Energy Physics

### Department/Division/Faculty:
High Energy Physics Group, Department of Physics

### Salary range:
Research Associate: £33,860 - £42,830 per annum (Maximum salary on appointment will be £33,860 per annum)

South Kensington Campus
 
Fixed Term: up to 11 months
 
The High Energy Physics Group at Imperial College London invites applications for a Research Associate to work on a joint project with Royal 
Holloway University of London. The postholder will work on R&D for a future high-pressure gas TPC (HPTPC) comprising hardware, software and 
analysis work, and development of Hyper-Kamiokande detector calibration systems. This will involve working with a team applying 
multidisciplinary skills in the general areas software, hardware, computing and analysis. The Imperial College HK group is playing important 
roles in near detector design and far detector calibration.
 
A PhD in Experimental Particle Physics or equivalent professional qualifications and experience is essential as is experience in HEP and/or 
neutrino data analysis, and evidence of good problem-solving skills.. Experience in taking initiative and/or developing own ideas 
independently, and experience in leadership or evidence of future leadership potential, are also essential.
 
Experience of programming in C++, working with hardware development and/or maintenance, detector/accelerator operations and performance 
studies, and experience of Monte Carlo simulation development and use are desirable. Experience of working with Postgraduate or advanced 
Undergraduate students, and of working in an international collaborative environment are also desirable.
 
Work will be carried out in London. Other UK and foreign travel is also likely. The postholder will be expected to contribute to the 
Department's teaching activities up to approximately half a day per week during the academic year, as appropriate.
 
Further details about the post are available from Dr Morgan Wascko, Senior Lecturer (m.wascko@imperial.ac.uk).
 
The Imperial College London High Energy Physics group has a strong experimental programme encompassing the CMS and LHCb experiments at the LHC 
and the T2K experiment in Japan.  The group is also active in searches for Dark Matter, SuperNEMO, LISA, the development of future experiments 
and has an active accelerator programme. Further details may be found at: http://www.imperial.ac.uk/highenergyphysics

Closing Date:
04 November 2015 (midnight GMT)

How To Apply
Our preferred method of application is online via this website. Please download the following application form and save to your computer. Once 
completed, please upload your application form prior to submitting your application also providing a CV and a list of publications, and the 
names of three referees. Make sure to address all of the essential criteria in the application.

